---
title: "A replication study of the Mining Android Sandboxes research for malware detection"
author: "Rodrigo Bonifácio et al."
date: '2023-01-23'
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=5, fig.height=5, fig.path='./figures/', dev=c('png', 'pdf'))
setwd(".")
library(sqldf)
library(xtable)
```

# Setup and Exploratory Analysis

### Loading and cleaning up the datasets

```{r fullDataSet}
full_ds <- read.csv("large_ds.csv", head=T, sep=',')
small_ds <- read.csv("small_ds.csv", head=T, sep=',')
full_ds$similarity = as.numeric(as.character(full_ds$similarity))
#full_ds = sqldf("select * from full_ds where family in (select family from small_ds where family <> 'None')
#                and family <> 'gappusin'")
```

### Showing the number of rows in the datasets

```{r number-of-rows}
nrow(full_ds)
nrow(small_ds)
```

### Number of malicious samples (LargeDS)

```{r countMalwareCDS}
sqldf("select malware, count(*) from full_ds group by malware")
```

### Number of repackaged apps classified as malware (LargeDS)

```{r countLabeledAsMalwareLargeDS}
sqldf("select apidetected, count(*) from full_ds group by apidetected")

sqldf("select malware, apidetected, count(*) 
       from full_ds 
       group by malware, apidetected")
```

### Number of repackaged apps classified as malware (SmallDS)

```{r countLabeledAsMalwareSmallDS}
sqldf("select apidetected, count(*) from small_ds group by apidetected")

sqldf("select malware, apidetected, count(*) 
       from small_ds 
       group by malware, apidetected")
```

# Small Dataset Assessment

### Accuracy Assessment (SmallDS)

```{r accuracySmallDS}
sqldf("select malware, apidetected, count(*) 
       from small_ds 
       group by malware, apidetected")


rp <- sqldf("select count(*) from small_ds where malware = 'True'")

tp <- sqldf("select * from small_ds where malware = 'True' and apidetected = 'True'" )

fp <- sqldf("select * from small_ds where malware = 'False' and apidetected = 'True'" )

fn <- sqldf("select * from small_ds where malware = 'True' and apidetected = 'False'" )

precision = nrow(tp) / (nrow(tp) + nrow(fp))

recall = nrow(tp) / (nrow(tp) + nrow(fn))

fscore = 2 * (precision*recall) / (precision + recall)

precision
recall
fscore
```

### Similarity Assessment (SmallDS)

```{r similaritySmallDS}
summary(small_ds$similarity)
sd(small_ds$similarity)
```

### Distribution of the malware families (SmallDS)

```{r smallDSFamilies}
total <- nrow(small_ds) 

totalNoFamily <- nrow(sqldf("select * from small_ds where family = 'None'"))

percentageWithFamily <- 100 - (totalNoFamily * 100 / total)

percentageWithFamily

families <- sqldf("select family, count(*) as Total 
                   from small_ds where family != 'None'
                   group by family 
                   order by 2 desc")

families["Percentage"] <- families$Total * 100 / percentageWithFamily

sqldf("select family, percentage from families order by 2 desc")
```

# Large Dataset Assessment

### Accuracy Assesment (LargeDS)

```{r accuracyLargeDS}
tp <- sqldf("select * from full_ds where malware = 'True' and apidetected = 'True'" )

fp <- sqldf("select * from full_ds where malware = 'False' and apidetected = 'True'" )

fn <- sqldf("select * from full_ds where malware = 'True' and apidetected = 'False'" )

precision = nrow(tp) / (nrow(tp) + nrow(fp))

recall = nrow(tp) / (nrow(tp) + nrow(fn))

fscore = 2 * (precision*recall) / (precision + recall)

precision
recall
fscore
```

### Similarity Assessment (LargeDS)

```{r similarityLargeDS}
summary(full_ds$similarity)
sd(full_ds$similarity)

sqldf("select count(*) from full_ds where similarity = 0")

sqldf("select count(*) from full_ds where similarity < 0.25")
sqldf("select count(*)  from full_ds where similarity >= 0.25 and similarity < 0.5")
sqldf("select count(*)  from full_ds where similarity >= 0.5 and similarity < 0.75")
sqldf("select count(*)  from full_ds where similarity >= 0.75")
sqldf("select count(*)  from full_ds where similarity >= 0.90")
```

### Logistic Regression on Similarity (LargeDS)

```{r glm}
#s1 <- sqldf("select ds.*, 'True' as h1 
#             from full_ds ds 
#             where (malware = 'True' and apidetected = 'True') or 
#                   (malware = 'False' and apidetected = 'False')")

s1 <- sqldf("select ds.*, 'True' as h1 
             from full_ds ds 
             where (malware = 'True' and apidetected = 'True')")

s2 <- sqldf("select ds.*, 'False' as h1 
             from full_ds ds
             where (malware = 'True' and apidetected = 'False') or 
                   (malware = 'False' and apidetected = 'True')")

ds <- rbind(s1, s2)

ds$h1 <- as.factor(ds$h1)

# cor.test(ds$h1, ds$similarity)

nrow(ds)

sqldf("select h1, count(*) from ds group by h1")

model <- glm(h1~similarity, data=ds, family = "binomial")

summary(model)
```

### Clustering Assessment on Similarity (LargeDS)

```{r clusterinigSimilarity}
set.seed(123)

km.res <- kmeans(ds$similarity, 10)


print(km.res$centers)

dd <- cbind(ds, cluster = km.res$cluster)


s1 <- sqldf("select cluster, count(*) as total from dd group by cluster")
s2 <- sqldf("select cluster, count(*) as hits from dd where h1 = 'True' group by cluster")

dd = merge(s1, s2)

dd["Percentage"] = dd$hits * 100 / dd$total

dd 

cs = data.frame("cluster" = c(1,2,3,4,5, 6, 7, 8, 9, 10), 
                "averageSimilarity" = km.res$centers)

cs = merge(dd, cs)

colnames(cs)

xtable(sqldf("select cluster, averageSimilarity, total, hits, percentAGE 
              from cs 
              order by averageSimilarity"))
```


# Comparing the similarity scores (LargeDS and SmallDS)

```{r similarityComparison}
summary(small_ds$similarity)
summary(full_ds$similarity)

sd(small_ds$similarity)
sd(full_ds$similarity)


sds <- sqldf("select similarity, 'Small Dataset' as dataset from small_ds") 
cds <- sqldf("select similarity, 'Complete Dataset' as dataset from full_ds") 

ds <- rbind(sds, cds)

ds$dataset <- factor(ds$dataset , levels=c("Small Dataset", "Complete Dataset"))

boxplot(similarity~dataset, data = ds, xlab="Datasets", ylab="Similarity Score", col = c("gray"), outline=F)
```


# Extensions' Assessments

### Accuracy Assesment (LargeDS with Parameter Extension)

```{r accuracyLargeDS-parameter}

tp <- sqldf("select * from full_ds where malware = 'True' and (apidetected = 'True' or paramdetected = 'True')" )

fp <- sqldf("select * from full_ds where malware = 'False' and (apidetected = 'True' or paramdetected = 'True')" )

fn <- sqldf("select * from full_ds where malware = 'True' and (apidetected = 'False' and paramdetected = 'False')" )

precision = nrow(tp) / (nrow(tp) + nrow(fp))

recall = nrow(tp) / (nrow(tp) + nrow(fn))

fscore = 2 * (precision*recall) / (precision + recall)

precision
recall
fscore
nrow(tp)
nrow(fp)
nrow(fn)
```

### Accuracy Assesment (LargeDS with Trace Extension)

```{r accuracyLargeDS-trace}

tp <- sqldf("select * from full_ds where malware = 'True' and (apidetected = 'True' or tracedetected = 'True')" )

fp <- sqldf("select * from full_ds where malware = 'False' and (apidetected = 'True' or tracedetected = 'True')" )

fn <- sqldf("select * from full_ds where malware = 'True' and (apidetected = 'False' and tracedetected = 'False')" )

precision = nrow(tp) / (nrow(tp) + nrow(fp))

recall = nrow(tp) / (nrow(tp) + nrow(fn))

fscore = 2 * (precision*recall) / (precision + recall)

precision
recall
fscore
nrow(tp)
nrow(fp)
nrow(fn)
```

### Accuracy Assesment (LargeDS with Trace and Parameter Extensions)

```{r accuracyLargeDS-parameter-trace}

tp <- sqldf("select * from full_ds where malware = 'True' and (apidetected = 'True' or tracedetected = 'True' or paramdetected = 'True')" )

fp <- sqldf("select * from full_ds where malware = 'False' and (apidetected = 'True' or tracedetected = 'True' or paramdetected = 'True')" )

fn <- sqldf("select * from full_ds where malware = 'True' and (apidetected = 'False' and tracedetected = 'False' and paramdetected = 'False')" )

precision = nrow(tp) / (nrow(tp) + nrow(fp))

recall = nrow(tp) / (nrow(tp) + nrow(fn))

fscore = 2 * (precision*recall) / (precision + recall)

precision
recall
fscore
nrow(tp)
nrow(fp)
nrow(fn)
```





# Gappusin and Revmob Assessment 

### Accuracy Assesment (LargeDS without samples from the Gappusin and Revmob family)

```{r accuracyCDSWithoutGappusin}

sqldf("select malware, apidetected, count(*) 
       from full_ds 
       where family = 'gappusin'
       group by malware, apidetected")

tp <- sqldf("select * from full_ds where malware = 'True' and apidetected = 'True' and family 
            
            not in ('revmob','gappusin')
            
            
            
            ")

fp <- sqldf("select * from full_ds where malware = 'False' and apidetected = 'True'")

fn <- sqldf("select * from full_ds where malware = 'True' and apidetected = 'False' and family
            not in ('revmob','gappusin')
            
            
            ") 


precision = nrow(tp) / (nrow(tp) + nrow(fp))

recall = nrow(tp) / (nrow(tp) + nrow(fn))

fscore = 2 * (precision*recall) / (precision + recall)

precision
recall
fscore
```

### Similarity Assessment (samples from the Gappusing family only)

```{r, similarityGappusin}

gappusin <- sqldf("select * from full_ds where family =  'gappusin'")

summary(gappusin$similarity)
sd(gappusin$similarity)
hist(gappusin$similarity, main="", xlab="Similarity Score", ylab="Frequency", col = c("gray"))
```
### Family Assessment

```{r familyAssesmentCDS}
sqldf("select family, count(*) 
       from full_ds 
       where malware = 'True' 
       group by family order by 2 desc")


sqldf("select malware, apidetected, count(*) 
       from full_ds 
       where family = 'gappusin'
       group by malware, apidetected")

sqldf("select count(distinct family) from full_ds")


totalWithFamily <- nrow(sqldf("select * from full_ds where malware = 'True'"))

families <- sqldf("select family, count(*) as Total 
                   from full_ds 
                   group by family 
                  order by 2 desc")

families["Percentage"] <- families["Total"] * 100 / totalWithFamily
sqldf("select family, Percentage
       from families where family <> 'None'
       order by 2 desc")
```


# Additional Assessments

## Accuracy Assesment 

```{r accuracyCDS-just-one-vendor}

tp <- sqldf("select * from full_ds where (malware = 'True' or qtdvendor = 1) and apidetected = 'True'")

fp <- sqldf("select * from full_ds where (malware = 'False' and qtdvendor = 0) and apidetected = 'True'")

fn <- sqldf("select * from full_ds where (malware = 'True' or qtdvendor = 1) and apidetected = 'False'" )

precision1V = nrow(tp) / (nrow(tp) + nrow(fp))

recall1V = nrow(tp) / (nrow(tp) + nrow(fn))

fscore1V = 2 * (precision1V*recall1V) / (precision1V + recall1V)

precision1V
recall1V
fscore1V
```
