---
title: "Dataset Merge"
author: "Francisco Handrick"
date: '2024-20-03'
output: html_document
description: This script create our final dataset file for analysis - sample_final_ds_before_VT_check.csv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=5, fig.height=5, fig.path='./figures/', dev=c('png', 'pdf'))

setwd(".")

library(sqldf)
library(xtable)
```

## Merge Script


The purpose of this R script is to merge several datasets into a single one. 
The following datasets are merged:

   * *appsHash* contains the hash of all apps, including information to indicate 
   if a given asset is an original or a repackaged version of an app. 
   
   * *avclass* contains the results of using the tool av2class to identify 
   the family of the malware in our dataset. 
   
   * *sampleAppHash.csv* contains the hash of the original apps used in our study. 
   
   * *originalSampleFamily* contains the malware family of the original apps used in our study. 
   
   * *repackageSampleFamily.csv* contains the malware family of the repackage apps used in our study. 
   
   * *summary.csv* contains the outputs of the mining android sandbox approach.
   
   * *summarySimiDroid.csv* contains the outputs of Simidroid with similarity of all app pairs.
   
We merge the above datasets and export the results to a file named *sample_final_ds_before_VT_check.csv*.   

```{r vt}

#Load the Datasets
apps <- read.csv("appsHash.csv", head=T, sep=',')

repackaged <- sqldf("select repackaged from apps ")

colnames(repackaged)
colnames(apps)


avclass <- read.csv("avClassResultRepackaged.csv", head=T, sep=',')
nrow(avclass)

result <- read.csv("../methods_explored/output/diffs/summary.csv")
result <- sqldf("select * from result")


apphash <- read.csv("sampleAppHash.csv", head=T, sep=',')
apphash <- sqldf("select * from apphash")
nrow(apphash)

firstPart <- sqldf("select h.dataset as source, h.hash as sha256original, h2.hash as sha256,
              case
	               when (r.methods_in_diff = '0') THEN 'False'
	                  Else 'True' 
	             END as apidetected

               from result r 
               inner join apphash h on h.app = r.apk
               inner join apphash h2 on h2.app = r.apk
               
               where h.type = 'benign' and h2.type = 'malicious'")


simiResults <- read.csv("summarySimiDroid.csv", head=T)
simiResults <- sqldf("select * from simiResults")

secondPart <- sqldf("select f.source, f.sha256original, f.sha256,f.apidetected,s.identical, s.similar, s.new, s.deleted, s.similarity from firstPart f 
               inner join simiResults s on s.sha256original = f.sha256original and s.sha256 = f.sha256")

originalFamily <- read.csv("originalSampleFamily.csv", head=T, sep=',')
originalFamily <- sqldf("select * from originalFamily ")

malwareFamily <- read.csv("repackageSampleFamily.csv", head=T, sep=',')
malwareFamily <- sqldf("select * from malwareFamily")

vendorCkeck <- read.csv("vendorCkeck.csv", head=T, sep=',')
vendorCkeck <- sqldf("select * from vendorCkeck")

thirdPart <- sqldf("select se.source, se.sha256original, o.benign ,se.sha256, r.family, 
                    case
	                     when ((r.family = 'None' and v.qtdvendor = '0') 
	                                  or (r.family = 'None' and v.qtdvendor = '1'))THEN 'False'
	                  Else 'True'
                     END as malware,v.qtdvendor as qtdvendor,
               se.apidetected,se.identical, se.similar, se.new, se.deleted, se.similarity from secondPart se 
               left join originalFamily o on o.hash = se.sha256original
               left join malwareFamily r on r.sha256repackage = se.sha256
               inner join vendorCkeck v on v.hash = se.sha256")

param_trace_diff <- read.csv("param_trace_diff.csv", head=T, sep=',')
param_trace_diff <- sqldf("select * from param_trace_diff ")

lastPart <- sqldf("select t.source as source, t.sha256original as sha256original, t.benign as benign, t.sha256 as sha256, 
                t.family as family, t.malware as malware,t.qtdvendor, t.apidetected as apidetected,tp.param_methods_in_diff as paramdetected, tp.trace_in_diff as tracedetected,                  t.identical as identical, t.similar as similar, t.new as new, t.deleted as deleted, t.similarity as similarity from thirdPart t 
                inner join param_trace_diff tp on tp.original = t.sha256original
                and tp.repackaged = t.sha256")


write.csv(lastPart, "sample_final_ds_before_VT_check.csv", quote = F, row.names = F)

large_ds = sqldf("select * from lastPart where benign = 'True'")

write.csv(large_ds, "large_ds.csv", quote = F, row.names = F)

```

```{r vt}





